---
title: "06-Recipes"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(AmesHousing)
library(tidymodels)
library(tune)
library(workflows)

ames <- make_ames() %>% 
  dplyr::select(-matches("Qu"))

set.seed(100)
ames_split <- initial_split(ames)
ames_train <- training(ames_split)
ames_test <- testing(ames_split)

fit_data <- function(object, model, data, ...) {
  if (inherits(object, "formula")) {
    object <- add_model(add_formula(workflow(), object, blueprint = hardhat::default_formula_blueprint(indicators = FALSE, ...)))
  }
  fit(object, data, ...)
}

fit_split <- function(object, model, split, ...) {
  if (inherits(object, "formula")) {
    object <- add_model(add_formula(workflow(), object, blueprint = hardhat::default_formula_blueprint(indicators = FALSE)), model)
  }
  tune::last_fit(object, split, ...)
}

# pca_rec <- 
#   recipe(Sale_Price ~ ., data = ames) %>%
#     step_novel(all_nominal()) %>%
#     step_dummy(all_nominal()) %>%
#     step_zv(all_predictors()) %>%
#     step_center(all_predictors()) %>%
#     step_scale(all_predictors()) %>%
#     step_pca(all_predictors(), num_comp = 5)
```

# Your Turn 1

Write a recipe for the `Sale_Price ~ `. variables that:
1. Adds a novel level to all factors  
2. Convert all factors to dummy variables  
3. Catches any zero variance variables  
4. Centers all of the predictors  
5. Scales all of the predictors  
6. Computes the first 5 principal components  

Save the result as `pca_rec`  

```{r}

```


# Your Turn 2

Make a workflow that combines `pca_rec` and with `lm_spec`.

```{r}

```

# Your Turn 3

Try our pca workflow on `ames_split`. What is the RMSE?

```{r}

```

# Your Turn 4

The Box-Cox transformation provides an alternative to centering and scaling data. Modify the code below to build a new pca recipe that uses a box-cox transformation instead of centering and scaling the data. Then update `pca_wf` to use the new recipe.

*Hint: Guess. Use tab completion. Or visit <http://tidymodels.github.io/recipes/reference/index.html>.*

```{r eval = FALSE}
bc_rec <- 
  recipe(Sale_Price ~ ., data = ames) %>%
    step_novel(all_nominal()) %>%
    step_dummy(all_nominal()) %>%
    step_zv(all_predictors()) %>%
    step_center(all_predictors()) %>%
    step_scale(all_predictors()) %>%
    step_pca(all_predictors(), num_comp = 5)

bc_wf <- 
  pca_wf %>% 
    ____________(bc_rec)
```


# Your Turn 5

Add a recipe step to downsample the remote variable majority class in the training set prior to model training. Edit your workflow, then re-fit the model and examine the metrics. Is the ROC AUC better than chance (.5)?

```{r}
library(modeldata)
data(stackoverflow)

set.seed(100) # Important!
so_split <- initial_split(stackoverflow, strata = Remote)
so_train <- training(so_split)
so_test  <- testing(so_split)

tree_spec <- 
  decision_tree() %>%         
  set_engine("rpart") %>%      
  set_mode("classification") 

so_rec <- recipe(Remote ~ ., data = so_train) %>% 
  step_dummy(all_nominal(), -all_outcomes()) %>% 
  step_lincomb(all_predictors())

so_wf <- workflow() %>% 
  add_model(tree_spec) %>% 
  add_recipe(so_rec)

set.seed(1980)
so_wf %>% 
  fit_split(split = so_split) %>% 
  collect_metrics()
```

