---
title: "01-Prediction"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(AmesHousing)
library(tidymodels)
library(tune)

ames <- make_ames() %>% 
  dplyr::select(-matches("Qu"))

fit_data <- function(formula, model, data, ...) {
  wf <- workflows::add_model(workflows::add_formula(workflows::workflow(), formula), model)
  fit(wf, data, ...)
}

fit_split <- function(formula, model, split, ...) {
  wf <- workflows::add_model(workflows::add_formula(workflows::workflow(), formula, blueprint = hardhat::default_formula_blueprint(indicators = FALSE)), model)
  tune::last_fit(wf, split, ...)
}
```

# Your Turn 1

Work together in your team to fill out as much of the handout as you can. Feel free to leave some blank.

# Your Turn 2

Let's review the handout answers in light of our conversation.

# Your Turn 3

Write a pipe that creates a learner that uses `lm()` to fit a linear regression. Save it as `lm_spec` and look at the object. What does it return?

*Hint: you'll need https://tidymodels.github.io/parsnip/articles/articles/Models.html*

```{r}
lm_spec <- 
   linear_reg() %>% # Pick linear regression
   set_engine(engine = "lm") # set engine
lm_spec
```

# Your Turn 4

Double check. Does

```{r}
lm_fit <- fit_data(Sale_Price ~ Gr_Liv_Area, model = lm_spec, data = ames)
lm_fit
```

give the same results as

```{r}
lm(Sale_Price ~ Gr_Liv_Area, data = ames)
```

# Your Turn 5

Fill in the blanks. Use `predict()` to:

1. Use your linear model to predict sale prices; save the tibble as `price_pred`

2. Add a pipe and use `mutate()` to add a column with the observed sale prices; name it `truth`

*Hint: Be sure to remove every `_` before running the code!*

```{r}
lm_fit <- fit_data(Sale_Price ~ Gr_Liv_Area, 
                   model = lm_spec, 
                   data = ames)

price_pred <- lm_fit %>% 
  predict(new_data = ames) %>% 
  mutate(truth = ames$Sale_Price)

price_pred
```

# Your Turn 6

In your teams, decide which model:

1. Has the smallest residuals  
2. Will have lower prediction error. Why?  

# Your Turn 7

Fill in the blanks. Use `initial_split()`, `training()`, `testing()`, `fit_data()` and `predict()` to

1. Split ames into training and test sets. Save the rsplit!  
2. Extract the training data. Fit a linear model to it. Save the model!  
3. Extract the test data.  
4. Measure the RMSE of your linear model with your test set.  
5. Keep `set.seed(100)` at the start of your code.  

*Hint: Be sure to remove every `_` before running the code!*

```{r}
set.seed(100) # Important!

ames_split  <- initial_split(ames)
ames_train  <- training(ames_split)
ames_test   <- testing(ames_split)

lm_fit      <- fit_data(Sale_Price ~ Gr_Liv_Area, 
                        model = lm_spec, 
                        data = ames_train)

price_pred  <- lm_fit %>% 
  predict(new_data = ames_test) %>% 
  mutate(price_truth = ames_test$Sale_Price)

rmse(price_pred, truth = price_truth, estimate = .pred)
```



# Your Turn 8

Rewrite your code from the previous exercise using `fit_split()` and `collect_metrics()` to:

1. Split **ames** into training and test sets. Save the rsplit!

1. Fit a linear model to the training set, then use the model to predict new observations from the test set.

1. Extract the rmse- is it the same as what we just calculated in our previous exercise `53885`?


```{r}
set.seed(100) # Important!

ames_split <- initial_split(ames)

lm_split <- fit_split(Sale_Price ~ Gr_Liv_Area, 
                      model = lm_spec, 
                      split = ames_split)

lm_split %>% 
  collect_metrics()
```

# Your Turn 9

Write a pipe to create a model that uses the rpart package to fit a regression tree. Save it as `rt_spec` and look at the object. What does it return?

*Hint: you'll need https://tidymodels.github.io/parsnip/articles/articles/Models.html*

```{r}
rt_spec <- 
  decision_tree() %>%          
  set_engine(engine = "rpart") %>% 
  set_mode("regression")
rt_spec
```

# Your Turn 10

Use `fit_split()` and `collect_metrics()` again, this time to fit a regression tree model to the training data with formula = Sale_Price ~ Gr_Liv_Area; then predict new sale prices with the testing data. Compare the rmse here to one using the linear model for the same formula- which is better?

```{r}
set.seed(100) # Important!
fit_split(Sale_Price ~ Gr_Liv_Area, 
          model = lm_spec, 
          split = ames_split) %>% 
  collect_metrics()

set.seed(100) # Important!
fit_split(Sale_Price ~ Gr_Liv_Area, 
          model = rt_spec, 
          split = ames_split) %>% 
  collect_metrics()
```
