---
title: "01-Prediction"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(AmesHousing)
library(tidymodels)
library(tune)

ames <- make_ames() %>% 
  dplyr::select(-matches("Qu"))

fit_data <- function(formula, model, data, ...) {
  wf <- workflows::add_model(workflows::add_formula(workflows::workflow(), formula), model)
  fit(wf, data, ...)
}

fit_split <- function(formula, model, split, ...) {
  wf <- workflows::add_model(workflows::add_formula(workflows::workflow(), formula, blueprint = hardhat::default_formula_blueprint(indicators = FALSE, allow_novel_levels = TRUE)), model)
  tune::last_fit(wf, split, ...)
}
```

# Your Turn 1

Work together in your team to fill out as much of the handout as you can. Feel free to leave some blank.

# Your Turn 2

Let's review the handout answers in light of our conversation.

# Your Turn 3

Write a pipe that creates a learner that uses `lm()` to fit a linear regression. Save it as `lm_spec` and look at the object. What does it return?

```{r}
lm_spec <- 
   linear_reg() %>% # Pick linear regression
   set_engine(engine = "lm") # set engine
lm_spec
```

# Your Turn 4

Double check. Does

```{r}
lm_fit <- fit_data(Sale_Price ~ Gr_Liv_Area, model = lm_spec, data = ames)
lm_fit
```

give the same results as

```{r}
lm(Sale_Price ~ Gr_Liv_Area, data = ames)
```


# Your Turn 5

Challenge: can you fit the model that uses `Bedroom_AbvGr`, `Full_Bath` and `Half_Bath` to predict `Sale_Price`? Save the result as `bedbath_fit`.

```{r}
bedbath_fit <- fit_data(Sale_Price ~ Bedroom_AbvGr + Full_Bath + Half_Bath, model = lm_spec, data = ames)
bedbath_fit
```



# Your Turn 6

(Slide of overfit and appropriately fit models)
In your teams, decide which model:

1. Has the smallest residuals  
2. Will have lower prediction error. Why?  


# Your Turn 7

Fill in the blanks. Use `initial_split()`, `training()`, `testing()`, `fit_data()` and `predict()` to

1. Split ames into training and test sets. Save the rsplit!  
2. Extract the training data. Fit a linear model to it. Save the model!  
3. Extract the test data.  
4. Use your linear model to predict the values in your test set.  
5. Keep `set.seed(100)` at the start of your code.  

*Hint: Be sure to remove every `_` before running the code!*

```{r}
set.seed(100) # Important!
ames_split <- initial_split(ames)

ames_train <- training(ames_split)
lm_fit <- fit_data(Sale_Price ~ Gr_Liv_Area, 
                   model = lm_spec, 
                   data = ames_train)

ames_test <- testing(ames_split)
lm_pred <- predict(lm_fit, new_data = ames_test)
```



# Your Turn 8

Compute the test RMSE for our `Sale_Price ~ Bedroom_AbvGr + Full_Bath + Half_Bath` model. You will need to train the model on `ames_train` and use the result to predict the values of `ames_test`.

```{r}
bb_fit <- fit_data(Sale_Price ~ Bedroom_AbvGr + Full_Bath + Half_Bath, model = lm_spec, data = ames_train)

bb_pred <- predict(bb_fit, new_data = ames_test)

rmse_vec(truth = ames_test$Sale_Price, estimate = bb_pred$.pred)
```


# Your Turn 9

Wrap this all up with `fit_split()` and `collect_metrics()`.

```{r}
fit_split(Sale_Price ~ Bedroom_AbvGr + Full_Bath + Half_Bath, model = lm_spec, split = ames_split) %>% collect_metrics()
```


# Your Turn 10

Write a pipe to create a model that uses the rpart package to fit a regression tree. Save it as `rt_spec` and look at the object. What does it return?

```{r}
rt_spec <- 
  decision_tree() %>%          
  set_engine(engine = "rpart") %>% 
  set_mode("regression")
rt_spec
```

# Your Turn 11

Use `fit_split()` and `collect_metrics()` again, this time to fit a regression tree model to the training data with formula = Sale_Price ~ Gr_Liv_Area; then predict new sale prices with the testing data. Compare the rmse here to one using the linear model for the same formula- which is better?

```{r}
fit_split(Sale_Price ~ Gr_Liv_Area, 
          model = lm_spec, 
          split = ames_split) %>% 
  collect_metrics()

set.seed(100) # Important!
fit_split(Sale_Price ~ Gr_Liv_Area, 
          model = rt_spec, 
          split = ames_split) %>% 
  collect_metrics()
```


