---
title: "04-Ensembling"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(tidymodels)
library(tune)

fit_split <- function(formula, model, split, ...) {
  wf <- workflows::add_model(workflows::add_formula(workflows::workflow(), formula, blueprint = hardhat::default_formula_blueprint(indicators = FALSE)), model)
  tune::last_fit(wf, split, ...)
}
```

```{r}
# read in the data
stackoverflow <- read_rds(here::here("materials/data/stackoverflow.rds"))

# split the data
set.seed(100) # Important!
so_split <- initial_split(stackoverflow, strata = remote)
so_train <- training(so_split)
so_test  <- testing(so_split)
```


# Day One - How to get good predictions from models  

## 5. Ensembling

# Your turn 1

Group activity

1. Make 10 bootstrapped classification trees

1. Take single data point and run it through each tree - what class gets predicted each time?

# Your Turn 2

Group activity (continued)

Tally up your trees.

Calculate your team's accuracy.

Now we combine votes- wisdom of the crowd!

<!--start with random forest- no args-->

# Your Turn 3

Fill in the blanks. Use `fit_split()`, `metric_set()`, and `collect_predictions()` to

1. Fit a random forest model with the ranger package; use the formula `remote ~ .`
2. Set accuracy and roc_auc as the metrics.
3. Look at the predictions you've collected- what does each row represent?
4. Keep `set.seed(100)` - don't remove or change that number.  

*Hint: Be sure to remove every `_` before running the code!*


```{r}
rf_spec <- rand_forest() %>% 
  set_engine("ranger") %>% 
  set_mode("classification")

set.seed(100)
rf_fit <- fit_split(remote ~ ., 
                    model = rf_spec, 
                    split = so_split,
                    metrics = metric_set(accuracy, roc_auc)) 

rf_fit %>% 
  collect_predictions()
```

<!-- each row is the majority vote of several trees- how many?
We can't know for sure - only know total trees
Each tree sees ~63.2% of rows-->
<!-- key points: > .50 = remote; each row is the proportion of trees that voted for each outcome -->

# Your Turn 4

Use `collect_metrics()` and compare the area under the ROC curve to our single decision tree- what do you notice?

```{r}
rf_fit %>% 
  collect_metrics()
```


# Your Turn 5

Fill in the blanks. Use `collect_predictions()` and `roc_curve()` to

1. Calculate the data needed to construct the full ROC curve- remember you need to name the column with the true class, and the column with the class probabilities.

2. Examine the ROC curve tibble and plot- how are they different from the single decision tree?

3. If we wanted specificity to be greater than .9, what probability threshold would we choose? What is the highest value of sensitivity we think we can achieve in this case?

*Hint: Be sure to remove every `_` before running the code!*

```{r}
rf_roc <- rf_fit %>% 
  collect_predictions() %>% 
  roc_curve(remote, .pred_Remote)

rf_roc

rf_roc %>% 
  autoplot()
```

# Your Turn 6

Fill in the blank. Use `set_args()` to update your `rf_spec` to use 1, 2, 3, and 19 variables at each split. Which value maximizes the area under the ROC curve?

```{r}
rf_spec <- rf_spec %>% 
  set_args(mtry = 10)

set.seed(100)
rf_fit <- fit_split(remote ~ ., 
                    model = rf_spec, 
                    split = so_split,
                    metrics = metric_set(roc_auc)) 

rf_fit %>% 
  collect_metrics()
```


# Your Turn 7

add variable importance, try plotting it (this might be too much- perhaps move to slides only)

```{r}
rf_spec <- rand_forest() %>% 
  set_engine("ranger", importance = "permutation") %>% 
  set_mode("classification")

set.seed(100)
rf_fitwf <- fit_split(remote ~ ., 
                    model = rf_spec, 
                    split = so_split,
                    metrics = metric_set(roc_auc)) 

rf_fit <- rf_fitwf %>% 
  pluck(".workflow", 1) %>% 
  workflows::pull_workflow_fit() 

vip::vip(rf_fit, geom = "point")
```



---

ignore code here, testing things out

```{r}
# try just bagging without random forest
set.seed(100) # Important!
so_boots <- bootstraps(so_train)

# use same decision tree model spec
dt_spec <- 
  decision_tree() %>%          
  set_engine(engine = "rpart") %>% 
  set_mode("classification")
dt_spec

set.seed(100) # Important!
bdt_fit <- fit_resamples(remote ~ years_coded_job + salary, 
                    model = dt_spec, 
                    resamples = so_boots,
                    control = control_resamples(save_pred = TRUE)) 

bdt_fit %>% 
  collect_metrics(summarize = FALSE)

bdt_fit %>% 
  collect_metrics()

# must save predictions
bdt_fit %>%   
  collect_predictions()

# how many trees voted on row 1? How about row 6?
bdt_fit %>%   
  collect_predictions() %>% 
  count(.row)

# look at actual votes-
bdt_fit %>%   
  collect_predictions() %>% 
  janitor::tabyl(.row, .pred_class)
```


### Day One Recap: Avoid overfitting with data splitting

Data splitting means dividing your data into a training set to build your model and a test set to test your model against. This is a good idea because:

* **Test sets provide an unbiased estimate of performance accuracy** - Your model hasn’t seen the test set, it will need to predict it the same way it will need to predict future data.

* **Testing avoids overfitting** - Test accuracy will drop as soon as you begin overfitting your data, so improve your model until the test accuracy drops.