---
title: "07-CV"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(AmesHousing)
library(tidymodels)
library(tune)
library(workflows)

ames <- make_ames() %>% 
  dplyr::select(-matches("Qu"))

set.seed(100)
ames_split <- initial_split(ames)
ames_train <- training(ames_split)
ames_test <- testing(ames_split)

fit_data <- function(object, model, data, ...) {
  if (inherits(object, "formula")) {
    object <- add_model(add_formula(workflow(), object, blueprint = hardhat::default_formula_blueprint(indicators = FALSE, ...)))
  }
  fit(object, data, ...)
}

fit_split <- function(object, model, split, ...) {
  if (inherits(object, "formula")) {
    object <- add_model(add_formula(workflow(), object, blueprint = hardhat::default_formula_blueprint(indicators = FALSE)), model)
  }
  tune::last_fit(object, split, ...)
}
```

# Your Turn 1

Run the first code chunk. Then fill in the blanks to:

1. Create a split object that apportions 75% of `ames` to a training set and the remainder to a testing set.
2. Fit the `all_wf` to the split object.
3. Extract the rmse of the fit.

```{r}
lm_spec <- 
  linear_reg() %>% 
  set_engine("lm")

all_wf <- 
  workflow() %>% 
  add_formula(Sale_Price ~ .) %>% 
  add_model(lm_spec)

set.seed(100)
```

```{r}
new_split <- ___________(ames)
all_wf %>% 
  __________(split = new_split) %>% 
  collect_metrics()
```

Answer:

```{r}
new_split <- initial_split(ames)
all_wf %>% 
  fit_split(split = new_split) %>% 
  collect_metrics()
```

# Your Turn 2

What would happen if you repeated this process? Would you get the same answers? Discuss in your team. 

Note your answer from above. Then rerun just the last code chunk above. Do you get the same answer?

# Your Turn 3

Rerun the code below 10 times and then compute the mean of the results (so you will need to jot them down as you go).

```{r}
new_split <- initial_split(ames)
all_wf %>% 
  fit_split(split = new_split) %>% 
  collect_metrics() %>% 
  filter(.metric == "rmse") %>% 
  pluck(".estimate")
```

Answer:
```{r}
rmses <- vector(length = 10, mode = "double")
for (i in 1:10) {
  new_split <- initial_split(ames)
  rmses[i] <-
    all_wf %>% 
      fit_split(split = new_split) %>% 
      collect_metrics() %>% 
      filter(.metric == "rmse") %>% 
      pluck(".estimate")
}
rmses
mean(rmses)
```

## Your Turn 4

Run the code below. What does it return?

```{r}
set.seed(100)
cv_folds <- 
    vfold_cv(ames, v = 10, strata = Sale_Price, breaks = 4)
cv_folds
```

## Your Turn 5

Modify the code below to use `fit_resamples` and `cv_folds` to cross-validate the `all_wf` workflow. Which RMSE do you collect at the end?

```{r}
all_wf %>% 
  fit_split(split = new_split) %>% 
  collect_metrics()
```

Answer:
```{r}
all_wf %>% 
  fit_resamples(resamples = cv_folds) %>% 
  collect_metrics()
```

## Your Turn 6

Create two new workflows, one that fits the bedbath model, 
`Sale_Price ~ Bedroom_AbvGr + Full_Bath + Half_Bath` 
and one that fits the square foot model, 
`Sale_Price ~ Gr_Liv_Area`

Then use `fit_resamples` and `cv_folds` to compare the performance of each.

```{r}
bb_wf <- 
  ___________ %>% 
    __________(Sale_Price ~ Bedroom_AbvGr + Full_Bath + Half_Bath) %>% 
    __________(lm_spec)

sqft_wf <- 
  __________ %>% 
    _________________________ %>% 
    _________________________

bb_wf %>% 
  ____________________________ %>%  
  ____________________

sqft_wf %>% 
  ____________________________ %>% 
  ____________________
```

Answer:
```{r}
bb_wf <- 
  workflow() %>% 
    add_formula(Sale_Price ~ Bedroom_AbvGr + Full_Bath + Half_Bath) %>% 
    add_model(lm_spec)

sqft_wf <- 
  workflow() %>% 
    add_formula(Sale_Price ~ Gr_Liv_Area) %>% 
    add_model(lm_spec)

bb_wf %>% 
  fit_resamples(resamples = cv_folds) %>% 
  collect_metrics()

sqft_wf %>% 
  fit_resamples(resamples = cv_folds) %>% 
  collect_metrics()
```

## Your Turn 7

Work together with your teammates to complete the cross-validation handout.

## Your Turn 8

Modify the code below to return the **Mean Absolute Error.** Visit 
tidymodels.github.io/yardstick/reference/index.html to find the right function to use.

```{r}
bb_wf <- 
  workflow() %>% 
    add_formula(Sale_Price ~ Bedroom_AbvGr + Full_Bath + Half_Bath) %>% 
    add_model(lm_spec)

sqft_wf <- 
  workflow() %>% 
    add_formula(Sale_Price ~ Gr_Liv_Area) %>% 
    add_model(lm_spec)

bb_wf %>% 
  fit_resamples(resamples = cv_folds) %>% 
  collect_metrics()

sqft_wf %>% 
  fit_resamples(resamples = cv_folds) %>% 
  collect_metrics()
```

Answer:
```{r}
bb_wf <- 
  workflow() %>% 
    add_formula(Sale_Price ~ Bedroom_AbvGr + Full_Bath + Half_Bath) %>% 
    add_model(lm_spec)

sqft_wf <- 
  workflow() %>% 
    add_formula(Sale_Price ~ Gr_Liv_Area) %>% 
    add_model(lm_spec)

bb_wf %>% 
  fit_resamples(resamples = cv_folds, metrics = metric_set(mae)) %>% 
  collect_metrics()

sqft_wf %>% 
  fit_resamples(resamples = cv_folds, metrics = metric_set(mae)) %>% 
  collect_metrics()
```

