---
title: "08-Tune"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(AmesHousing)
library(tidymodels)
library(tune)
library(workflows)

ames <- make_ames() %>% 
  dplyr::select(-matches("Qu"))

set.seed(100)
ames_split <- initial_split(ames)
ames_train <- training(ames_split)
ames_test <- testing(ames_split)

fit_data <- function(object, model, data, ...) {
  if (inherits(object, "formula")) {
    object <- add_model(add_formula(workflow(), object, blueprint = hardhat::default_formula_blueprint(indicators = FALSE, ...)))
  }
  fit(object, data, ...)
}

fit_split <- function(object, model, split, ...) {
  if (inherits(object, "formula")) {
    object <- add_model(add_formula(workflow(), object, blueprint = hardhat::default_formula_blueprint(indicators = FALSE)), model)
  }
  tune::last_fit(object, split, ...)
}
```

# Your Turn 1

Combine the recipe and model below into a new workflow named `knn_wf`. Can you tell what type of model this uses?

Fit the workflow to `cv_folds` and collect its RMSE.

```{r}
normalize_rec <-
  recipe(Sale_Price ~ ., data = ames) %>% 
    step_novel(all_nominal()) %>% 
    step_dummy(all_nominal()) %>% 
    step_zv(all_predictors()) %>% 
    step_center(all_predictors()) %>% 
    step_scale(all_predictors())

knn5_spec <- 
  nearest_neighbor(neighbors = 5) %>% 
    set_engine("kknn") %>% 
    set_mode("regression")
```

Answer:
```{r}
knn5_wf <-
  workflow() %>% 
  add_recipe(normalize_rec) %>% 
  add_model(knn5_spec)

knn5_wf %>%
  fit_resamples(resamples = cv_folds) %>% 
  collect_metrics()
```

# Your Turn 2

Repeat the process in Your Turn 1 with a similar workflow that uses `neighbors = 10`. Does the RMSE change?

Answer:
```{r}
knn10_spec <- 
  nearest_neighbor(neighbors = 10) %>% 
    set_engine("kknn") %>% 
    set_mode("regression")

knn10_wf <-
  knn5_wf %>% 
  update_model(knn10_spec)

knn10_wf %>%
  fit_resamples(resamples = cv_folds) %>% 
  collect_metrics()
```

# Your Turn 3

Use `expand_grid()` to create a grid of values for `neighbors` that spans from 10 to 20. Save the result as `k10_20`.

Answer:
```{r}
k10_20 <- expand_grid(neighbors = 10:20)
```

# Your Turn 4

Create a knn workflow that tunes over `neighbors`. Then use `tune_grid`, `cv_folds` and `k10_20` to find the best value of `neighbors`. Save the output of `tune_grid`.

```{r}
knn_tuner <- 
  nearest_neighbor(neighbors = tune()) %>% 
    set_engine("kknn") %>% 
    set_mode("regression")

knn_twf <-
  workflow() %>% 
    add_recipe(normalize_rec) %>% 
    add_model(knn_tuner)

knn_results <- 
  knn_twf %>%
    tune_grid(resamples = cv_folds, grid = k10_20) 

knn_results %>% 
  collect_metrics() %>% 
  filter(.metric == "rmse")
```

# Your Turn 5

Modify our PCA workflow below to find the best value for `num_comp` on the grid provided. Which is it? Use `show_best()` to see. Save the output of the fit function as `pca_results`.

```{r}
lm_spec <- 
  linear_reg() %>% 
  set_engine("lm")

pca_rec <- 
  recipe(Sale_Price ~ ., data = ames) %>%
    step_novel(all_nominal()) %>%
    step_dummy(all_nominal()) %>%
    step_zv(all_predictors()) %>%
    step_center(all_predictors()) %>%
    step_scale(all_predictors()) %>%
    step_pca(all_predictors(), num_comp = 5)

pca_wf <-
  workflow() %>% 
    add_recipe(pca_rec) %>% 
    add_model(lm_spec)

nc10_40 <- expand_grid(num_comp = c(10,20,30,40))
```

Answer:
```{r}
lm_spec <- 
  linear_reg() %>% 
  set_engine("lm")

pca_tuner <- 
  recipe(Sale_Price ~ ., data = ames) %>%
    step_novel(all_nominal()) %>%
    step_dummy(all_nominal()) %>%
    step_zv(all_predictors()) %>%
    step_center(all_predictors()) %>%
    step_scale(all_predictors()) %>%
    step_pca(all_predictors(), num_comp = tune())

pca_twf <-
  workflow() %>% 
    add_recipe(pca_tuner) %>% 
    add_model(lm_spec)

nc10_40 <- expand_grid(num_comp = c(10,20,30,40))

pca_results <-
  pca_twf %>% 
    tune_grid(resamples = cv_folds, grid = nc10_40)

pca_results %>% 
  show_best(metric = "rmse", maximize = FALSE)
```

---

# Switch to Stackoverflow data

```{r}
library(modeldata)
data(stackoverflow)

# split the data
set.seed(100) # Important!
so_split <- initial_split(stackoverflow, strata = Remote)
so_train <- training(so_split)
so_test  <- testing(so_split)

set.seed(100) # Important!
so_folds <- vfold_cv(so_train, v = 10, strata = Remote)
```

---

# Your Turn 6

Edit the random forest model to tune the `mtry` and `min_n` hyper-parameters; call the new model spec `rf_tuner`.

Update the model for your workflow; save it as `rf_twf`.

Tune the workflow to `so_folds` and show the best combination of hyper-parameters to maximize `roc_auc`.

How does it compare to the average ROC AUC across folds from fit_resamples()?

```{r}
so_rec <- recipe(Remote ~ ., 
                 data = so_train) %>% 
  step_dummy(all_nominal(), -all_outcomes()) %>% 
  step_lincomb(all_predictors()) %>% 
  step_downsample(Remote)

rf_spec <- 
  rand_forest() %>% 
    set_engine("ranger") %>% 
    set_mode("classification")

rf_wf <-
  workflow() %>% 
    add_recipe(so_rec) %>% 
    add_model(rf_spec)
```

Answer:
```{r}
rf_tuner <- 
  rand_forest(mtry = tune(), min_n = tune()) %>% 
    set_engine("ranger") %>% 
    set_mode("classification")

rf_twf <-
  rf_wf %>% 
    update_model(rf_tuner)

rf_results <-
  rf_twf %>% 
    tune_grid(resamples = so_folds)
```

# Your Turn 7

Use `select_best()`, `finalize_workflow()`, and `fit_split()` to take the best combination of hyper-parameters from `rf_results` and use them to predict the test set.

How does our actual test ROC AUC compare to our cross-validated estimate?

```{r}
so_best <-
  rf_results %>% 
    select_best(metric = "roc_auc")

so_wfl_final <- 
  rf_twf %>%
    finalize_workflow(so_best)

so_test_results <-
  so_wfl_final %>% 
    fit_split(split = so_split)

so_test_results %>% 
  collect_metrics()
```

